---
title: "02 - Historic Segregation in St. Louis"
author: "Your Name"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: github_document
---

## Introduction
This notebook maps calculates segregation measures for each time period within the study.

## Dependencies
This notebook requires the following packages:

```{r load-packages}
# tidyverse packages
library(dplyr)
library(ggplot2)
library(tidyr)

# spatial packages
library(sf)

# other packages
library(DBI)
library(ggrepel)
```

```{r}
source(here::here("source", "functions", "get_coords.R"))
```


## Load Data
All of the historical data are stored in a SQLite database stored in this repository as a submodule. In addition, we'll need our census tract boundary data.

```{r load-data}
## establish SQLite connection
con <- dbConnect(RSQLite::SQLite(), here::here("data", "STL_DEMOGRAPHY_TractPop", "data", "STL_CITY_COUNTY_Database.sqlite"))

## tracts
tracts <- st_read(here::here("data", "STL_BOUNDARY_Tracts_2010", "STL_BOUNDARY_Tracts_2010.geojson")) %>%
  st_transform(crs = 26915) %>%
  rename(geoid = GEOID)
```

## Calculate Segregation
### 1940
In order to calculate the segregation measure ICE, we need to extract data on race out of the SQL database:

```{r collect-records-40}
## collect value
tbl(con, "population") %>%
  filter(year == "1940") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1940") %>%
  collect() -> race
```

The data are in "long" form, so we need to convert them to "wide" data before proceeding:

```{r pivot-40}
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)
```

Finally, we'll calculate ICE and then join it with our tract master object:

```{r ice-40}
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1940 = (white-black)/value) %>%
  select(geoid, ice_1940) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 1950
We'll repeat the process for 1950:

```{r segregation-50}
## collect value
tbl(con, "population") %>%
  filter(year == "1950") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1950") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1950 = (white-black)/value) %>%
  select(geoid, ice_1950) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 1960
We'll repeat the process for 1960:

```{r segregation-60}
## collect value
tbl(con, "population") %>%
  filter(year == "1960") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1960") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1960 = (white-black)/value) %>%
  select(geoid, ice_1960) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 1970
We'll repeat the process for 1970:

```{r segregation-70}
## collect value
tbl(con, "population") %>%
  filter(year == "1970") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1970") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1970 = (white-black)/value) %>%
  select(geoid, ice_1970) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 1980
We'll repeat the process for 1980:

```{r segregation-80}
## collect value
tbl(con, "population") %>%
  filter(year == "1980") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1980") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1980 = (white-black)/value) %>%
  select(geoid, ice_1980) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 1990
We'll repeat the process for 1990:

```{r segregation-90}
## collect value
tbl(con, "population") %>%
  filter(year == "1990") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "1990") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_1990 = (white-black)/value) %>%
  select(geoid, ice_1990) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 2000
We'll repeat the process for 2000:

```{r segregation-00}
## collect value
tbl(con, "population") %>%
  filter(year == "2000") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "2000") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_2000 = (white-black)/value) %>%
  select(geoid, ice_2000) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 2010
We'll repeat the process for 2010:

```{r segregation-10}
## collect value
tbl(con, "population") %>%
  filter(year == "2010") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "2010") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_2010 = (white-black)/value) %>%
  select(geoid, ice_2010) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

### 2018
We'll repeat the process for 2018:

```{r segregation-18}
## collect value
tbl(con, "population") %>%
  filter(year == "2018") %>%
  collect() -> pop

## collect race
tbl(con, "race") %>%
  filter(year == "2018") %>%
  collect() -> race

## pivot
race <- pivot_wider(race, names_from = "category", values_from = "value") %>%
  select(-year)

## calculate ice
left_join(pop, race, by = "geoid") %>%
  mutate(ice_2018 = (white-black)/value) %>%
  select(geoid, ice_2018) %>%
  left_join(tracts, ., by = "geoid") -> tracts
```

## Store Results
Next, we'll store our spatial data:

```{r store}
tracts %>%
  st_transform(crs = 4326) %>%
  st_write(here::here("results", "STL_DEMOGRAPHY_ICE", "STL_DEMOGRAPHY_ICE.geojson"), delete_dsn = TRUE)
```
 
## Create Map

```{r}
counties <- st_read(here::here("data", "STL_BOUNDARY_Counties", "STL_BOUNDARY_Counties.geojson")) %>%
  st_transform(crs = 26915)

symbolic_roads <- st_read(here::here("data", "STL_TRANS_Symbolic_Roads", "STL_TRANS_Symbolic_Roads.geojson")) %>%
  st_transform(crs = 26915) %>%
  filter(FULLNAME == "Delmar Blvd")

symbolic_roads_centroids <- symbolic_roads %>%
  st_centroid() %>%
  get_coords(crs = 26915)

symbolic_roads_centroids <- slice(symbolic_roads_centroids, 1)

tracts %>%
  select(geoid, ice_1940, ice_1950, ice_1970, ice_1990, ice_2010, ice_2018) %>%
  gather("period", "ice", ice_1940:ice_2018) %>%
  select(geoid, period, ice) %>%
  mutate(period = case_when(
   period == "ice_1940" ~ "1940", 
   period == "ice_1950" ~ "1950",
   period == "ice_1970" ~ "1970",
   period == "ice_1990" ~ "1990",
   period == "ice_2010" ~ "2010",
   period == "ice_2018" ~ "2018"
  )) %>%
  mutate(ice = ifelse(ice > 1, 1, ice)) -> tracts_long

categories <- cut(tracts_long$ice, breaks = seq(-1, 1, length.out = 7), include.lowest = TRUE, dig.lab = 2)

tracts_long <- mutate(tracts_long, cat = categories)

tracts_long$cat %>%
  forcats::fct_relabel(~ gsub(",", " to ", .x)) %>%
  forcats::fct_relabel(~ gsub("\\(", "", .x)) %>%
  forcats::fct_relabel(~ gsub("\\[", "", .x)) %>%
  forcats::fct_relabel(~ gsub("\\]", "", .x)) -> tracts_long$cat
```

```{r}
p <- ggplot(data = tracts_long, mapping = aes(fill = cat)) +
  geom_sf(size = .2) +
  geom_sf(data = counties, fill = NA, size = .6, color = "black") +
  geom_sf(data = symbolic_roads, fill = NA, size = 1, color = "white") +
  geom_text_repel(data = symbolic_roads_centroids, mapping = aes(x = x, y = y, label = FULLNAME, fill = NA),
                  nudge_x = -30000, nudge_y = 20000) +
  scale_fill_brewer(palette = "RdBu", name = "ICE") +
  cowplot::theme_map() +
  facet_wrap(~period, ncol = 2)

ggsave(here::here("results", "figures", "ice_multiples.png"), p, width = 7.5, height = 10.5, units = "in", dpi = 500)
```

